Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/inverted_u.tex
Minor edit.

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$ 
    & \makecell{\textbf{0.003}$\pm$0.003} 
    & \makecell{\textbf{0.083}$\pm$0.02} 
    & \makecell{\textbf{0.17}$\pm$0.02} \\\hline
$\DEG$ 
    & \makecell{\textbf{0.045}$\pm$0.01} 
    & \makecell{\textbf{0.25}$\pm$0.02} 
    & \makecell{\textbf{0.23}$\pm$0.02} \\\hline
$\DG$ 
    & \makecell{\textbf{0.12}$\pm$0.02} 
    & \makecell{\textbf{0.36}$\pm$0.03} 
    & \makecell{\textbf{0.3}$\pm$0.02} \\\hline
\end{tabular}
\label{ht_incum}
\caption{The temporary monopoly experiment with $X=200$ (and $T_0=\asedit{???}$), for the Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the row) and the incumbent's algorithm (the column). The cell specifies the entrant's market share for the rounds in which he was present. We give the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$ 
    & \makecell{\textbf{0.003}$\pm$0.003} 
    & \makecell{\textbf{0.083}$\pm$0.02} 
    & \makecell{\textbf{0.17}$\pm$0.02} \\\hline
$\DEG$ 
    & \makecell{\textbf{0.045}$\pm$0.01} 
    & \makecell{\textbf{0.25}$\pm$0.02} 
    & \makecell{\textbf{0.23}$\pm$0.02} \\\hline
$\DG$ 
    & \makecell{\textbf{0.12}$\pm$0.02} 
    & \makecell{\textbf{0.36}$\pm$0.03} 
    & \makecell{\textbf{0.3}$\pm$0.02} \\\hline
\end{tabular}
\label{ht_incum}
\caption{The temporary monopoly experiment with $X=200$ (and $T_0=\asedit{???}$), for the Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the {\bf row}) and the incumbent's algorithm (the {\bf column}). The cell specifies the entrant's market share for this game, over the rounds in which he was present. We give the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\end{table}
